Supplementary Materials- A Bayesian approach to burial networks to infer social changes in northeastern Taiwan during the European colonization period

### 2021-01-21 analysis/paper/supplementary-material.Rmd
stash

```{r explore-data, include=FALSE, cache=TRUE, cache.extra=tools::md5sum(here::here("analysis/paper/000-prep1-value-burials.R"))}
suppressWarnings(source(here::here("analysis", "paper", "000-prep2-goods-class-plot.R")))
```

@@

<!-- assessment of MCMC and Goodness-of-fit in Bayesian: move to SI -->
As an informal way to diagnose model convergence, we first evaluated three diagnostic visual summaries of our MCMC output, including density plots, trace plots, and autocorrelation plots [@Hamra2013], which we include in our Supplementary Online Materials. In general, we can see the informative prior contributed to a better convergence of the MCMC according to the diagnostic plots showing more stationary distributions and decreased autocorrelation. Then we summarize output from our two models by goodness-of-fit (GOF) diagnostics in the Bayesian framework, where the observed network is compared with the set of networks simulated from the estimated posterior distributions of the parameters of each model [@Caimo2011; @Caimo2017]. We set $`r bgof_si`$ network graphs simulated from the estimated posterior distribution in ERGMs. Our Bayesian GOF diagnostics summarized three distributions, including degree, minimum geodesic distance, and edgewise shared partner distributions. This provides a statistical approach to check how well the estimated posterior parameter distribution, based on our hypotheses, can reproduce networks with similar general structural features of the observed networks. We then compared the distribution of our observed networks, the networks before and after the arrival of Europeans, with the distribution of our hypothesized models. We expect to see the models fit with our hypotheses, indicative of a increased social inequality after the foreign contact. In addition, the covariates can give some more clues for the underlying mechanisms for the formations of each network, such as the relative importance of age and sex.

>>>>

```{r explore-data, include=FALSE, cache=TRUE, cache.extra=tools::md5sum(here::here("analysis/paper/000-prep2-goods-class-plot.R"))}
suppressWarnings(source(here::here("analysis", "paper", "000-prep2-goods-class-plot.R")))
```

```{r tidy-data, include=FALSE, cache=TRUE, cache.extra=tools::md5sum(here::here("analysis/paper/001-data-tidy.R"))}
suppressWarnings(source(here::here("analysis", "paper", "001-data-tidy.R")))
```

```{r burial-location, include=FALSE, cache=TRUE, cache.extra=tools::md5sum(here::here("analysis/paper/002-burial-location.R"))}
suppressWarnings(source(here::here("analysis", "paper", "002-burial-location.R")))
```

@@

<!-- assessment of MCMC and Goodness-of-fit in Bayesian: move to SI -->

```{r tidy-data, include=FALSE, cache=TRUE, cache.extra=tools::md5sum(here::here("analysis/paper/001-data-tidy.R"))}
suppressWarnings(source(here::here("analysis", "paper", "001-data-tidy.R")))
```

```{r bergm-pre, include=FALSE, cache=TRUE, cache.extra=tools::md5sum(here::here("analysis/paper/003-burials-pre-network-modelling.R"))}
suppressWarnings(source(here::here("analysis", "paper", "003-burials-pre-network-modelling.R")))
```

```{r bergm-post, include=FALSE, cache=TRUE, cache.extra=tools::md5sum(here::here("analysis/paper/004-burials-post-network-modelling.R"))}
suppressWarnings(source(here::here("analysis", "paper", "004-burials-post-network-modelling.R")))
```

```{r diag-plots}
png(filename = here::here("analysis", "figures", "008-pre-diag.png"),
    width = 10, height = 8, units = "in", res = 360)
plot(pre_bergm)
dev.off()
```

As an informal way to diagnose model convergence, we first evaluated three diagnostic visual summaries of our MCMC output, including density plots, trace plots, and autocorrelation plots [@Hamra2013], which we include in our Supplementary Online Materials. In general, we can see the informative prior contributed to a better convergence of the MCMC according to the diagnostic plots showing more stationary distributions and decreased autocorrelation. Then we summarize output from our two models by goodness-of-fit (GOF) diagnostics in the Bayesian framework, where the observed network is compared with the set of networks simulated from the estimated posterior distributions of the parameters of each model [@Caimo2011; @Caimo2017]. We set $`r bgof_si`$ network graphs simulated from the estimated posterior distribution in ERGMs. Our Bayesian GOF diagnostics summarized three distributions, including degree, minimum geodesic distance, and edgewise shared partner distributions. This provides a statistical approach to check how well the estimated posterior parameter distribution, based on our hypotheses, can reproduce networks with similar general structural features of the observed networks. We then compared the distribution of our observed networks, the networks before and after the arrival of Europeans, with the distribution of our hypothesized models. We expect to see the models fit with our hypotheses, indicative of a increased social inequality after the foreign contact. In addition, the covariates can give some more clues for the underlying mechanisms for the formations of each network, such as the relative importance of age and sex.
